The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-09-02 paper/Analisis.tex
Fixed peak maxima plot in the paper
short paragram on anisotripic emission

\begin{figure}
    \includegraphics[width=0.45\textwidth]{maximumvsVmax.png}
\caption{Position of the peak maxima as a function of rotational
  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
  homogeneous (central) source distributions. A value of $x_{\rm
    max}=0$ indicates that line becomes single
  peaked. \label{fig:maximumsvsvelocity}}  
\end{figure}

@@

\subsection{Different line of sights}

>>>>

\begin{figure}
    \includegraphics[width=0.45\textwidth]{maximumVvsVmax.png}
\caption{Position of the peak maxima as a function of rotational
  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
  homogeneous (central) source distributions. A value of $x_{\rm
    max}=0$ indicates that line becomes single
  peaked. \label{fig:maximumsvsvelocity}}  
\end{figure}

@@

\subsection{Anisotropic emission}

We study the deviations of the received flux on the surface of the
sphere. We follow \cite{Zheng2013} to estimate the flux seen by an
observer located at an angle $\Theta$ (distant observer angle)
normalized to the isotropic flux:

\begin{equation}
F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
\end{equation}
%
where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
$\Delta N$ is the number of photons in a angular bin $\Delta
\Theta$. This definition satifies the condition
$int_{-1}^{1}F(\mu)d\mu/2=1$.

In Figure 2 we show the angular dependencty of the flux for the
central (left) and homogeneous (right) source distributions. This
shows that observers at different directions would infer luminosities
different from the isotropical value only at levels $< 3\%$.
